Creating a Testing Framework and Workflow for Developers New to Web Application Engineering

### 2014-07-24 Paper/paper.tex
Next round of Cal Poly edits

% A Survey of Web Testing Frameworks and Workflow for Testing JavaScript Applications, Developing A Workflow for new Web Developers, 
\title{Creating a Testing Framework and Workflow for Developers New to Web Application Engineering} %\vfill gives us the black space at the top of the page
\author{Taggart Ashby}
\degreemonth{June} \degreeyear{2014} \degree{Master of Science}
\defensemonth{June} \defenseyear{2014}
\numberofmembers{3} \chair{Michael Haungs, Ph.D.\newline Professor of Computer Science} \othermemberA{Franz Kurfess, Ph.D.\newline Professor of Computer Science} \othermemberB{David Janzen, Ph.D.\newline Professor of Computer Science} \field{Computer Science} \campus{San Luis Obispo}
\copyrightyears{seven}

@@

Client-side programming is done in a language that the browser understands, most frequently JavaScript. Though not technically programming languages, client-side programming is also done through HTML and CSS which control the look and feel of web pages.

@@

\begin{Figure}
  \centering
  \includegraphics[width=0.75\linewidth]{todo_home.png} 
  \captionof{figure}{ToDo app home page, simple three-button naviagation} 
\end{Figure}

@@

Here is the new project page:
\begin{Figure}
  \centering
  \includegraphics[width=0.75\linewidth]{magnumCI_new_project.png}
\end{Figure}

Fill out the fields with the appropriate values for a given project and click ``Create Project''. Depending on what the setup is for your project, you'll see slightly varying web pages after you create your project. One thing in common, though, is the button at the bottom of the steps list that says ``Customize Build''. After following the instructions, click ``Customize Build'':
\begin{Figure}
  \centering
  \includegraphics[width=0.75\linewidth]{magnumCI_customize_build.png}
\end{Figure}

There are a number of configuration options and panes that can be accessed on the left side. Our focus was making sure the ``Build Configuration'' tab was properly set up. This involved selecting the correct branch, the correct Node.js runtime version, the correct database from the ``Resources'' area, and adding the appropriate commands in the build steps. In our case we wanted ``mongoDB'' and ``Xvfb'' for UI testing, and then \lstinline{NPM install -g} in the ``Dependencies Installation'' to make sure our modules are available when we need them. Finally, we run Nightwatch using \lstinline{nightwatch -c nightwatch.json} (the nightwatch flags will be outlined in the next section) in the ``Test suite commands'' box. All of that makes our build configuration page look like this:
\begin{Figure}
  \centering
  \includegraphics[width=0.75\linewidth]{magnumCI_customize_build_filled.png}
\end{Figure}

@@

To run Nightwatch, navigate to the project folder and run \lstinline{nightwatch -c path_to_nightwatch_config}. This will use the \lstinline{src_folders} attribute to determine where to look for the tests, start the Selenium server, and run the tests. When debugging certain functions of even test cases, tests can be isolated with the \lstinline{-t} flag: \lstinline{nightwatch -c nightwatch.json -t folder1/test1.js}. Nightwatch offers a number of other command-line arguments that are discussed in their developer guide \cite{NightwatchJS}.

@@

Not all of those tools made it into the eventual final toolkit, but they were all important to look at in the context of making the overarching toolkit.

@@

This step-by-step walkthrough of how to test was an excellent starting point to look at different tools and how they handled this issue.

>>>>

% A Survey of Web Testing Frameworks and Workflow for Testing JavaScript Applications, Developing A Workflow for new Web Developers, 
\title{Creating a Testing Framework and Workflow for Developers New to Web Application Engineering} %\vfill gives us the black space at the top of the page
\author{Taggart Ashby}
\degreemonth{June} \degreeyear{2014} \degree{Master of Science}
\defensemonth{June} \defenseyear{2014}
\numberofmembers{3} \chair{Michael Haungs, Ph.D.\newline Associate Professor of Computer Science} \othermemberA{Franz Kurfess, Ph.D.\newline Professor of Computer Science} \othermemberB{David Janzen, Ph.D.\newline Professor of Computer Science} \field{Computer Science} \campus{San Luis Obispo}
\copyrightyears{seven}

@@

Client-side programming is done in a language that the browser understands, most frequently JavaScript. Though not technically programming languages, client-side programming is also done through HTML and CSS.

@@

\begin{Figure}
  \centering
  \includegraphics[width=0.75\linewidth]{todo_home.png} 
  \captionof{figure}{ToDo app home page, simple three-button navigation} 
\end{Figure}

@@

Here is the new project page:
\begin{Figure}
  \centering
  \includegraphics[width=0.75\linewidth]{magnumCI_new_project.png}
  \captionof{figure}{MagnumCI new project screen}
\end{Figure}

Fill out the fields with the appropriate values for a given project and click ``Create Project''. Depending on what the setup is for your project, you'll see slightly varying web pages after you create your project. One thing in common, though, is the button at the bottom of the steps list that says ``Customize Build''. After following the instructions, click ``Customize Build'':
\begin{Figure}
  \centering
  \includegraphics[width=0.75\linewidth]{magnumCI_customize_build.png}
  \captionof{figure}{MagnumCI build customization}
\end{Figure}

There are a number of configuration options and panes that can be accessed on the left side. Our focus was making sure the ``Build Configuration'' tab was properly set up. This involved selecting the correct branch, the correct Node.js runtime version, the correct database from the ``Resources'' area, and adding the appropriate commands in the build steps. In our case we wanted ``mongoDB'' and ``Xvfb'' for UI testing, and then \lstinline{NPM install -g} in the ``Dependencies Installation'' to make sure our modules are available when we need them. Finally, we run Nightwatch using \lstinline{nightwatch -c nightwatch.json} (the nightwatch flags will be outlined in the next section) in the ``Test suite commands'' box. All of that makes our build configuration page look like this:
\begin{Figure}
  \centering
  \includegraphics[width=0.75\linewidth]{magnumCI_customize_build_filled.png}
  \captionof{figure}{MagnumCI example build}
\end{Figure}

@@

To run Nightwatch, navigate to the project folder and run \lstinline{nightwatch -c} \newline \lstinline{path_to_nightwatch_config}. This will use the \lstinline{src_folders} attribute to determine where to look for the tests, start the Selenium server, and run the tests. When debugging certain functions of even test cases, tests can be isolated with the \lstinline{-t} flag: \lstinline{nightwatch -c nightwatch.json -t folder1/test1.js}. Nightwatch offers a number of other command-line arguments that are discussed in their developer guide \cite{NightwatchJS}.

@@

@@
